Chemically Dependent Selectivity in a Cross-linked H\textsubscript{II} Phase Lyotropic Liquid Crystal Membrane

### 2019-03-19 Ben_Manuscripts/transport/Outline.tex
Outline updates

  The Stokes-Einstein relationship expresses the diffusion coefficient of 
  a hard spherical particle as a function inversely related to its radius.
  \begin{itemize}
  	\item $D = \dfrac{k_bT}{6\pi\eta r}$ where $k_b$ and $T$ are Boltzmann
  	constant and the system temperature respectively and $\eta$ is the 
  	system's viscosity.
  	\item For calculation relevant to this study, we assume that the viscosity
  	is constant.
  	\item Additionally, we will apply the relationship to solute MSDs which is
  	valid because all trajectories are of the same length.
  	\item It is well-known that the relationship breaks down when solute size becomes
  	on the order of solvent size because the solute can no longer be treated
  	as a non-interacting hard sphere. 
  \end{itemize}

  Gierer and Wirtz introduced a microfriction correction factor in order to 
  address this issue. 
  \begin{itemize}
    \item They proposed that $D = \dfrac{k_bT}{6\pi\eta fr}$
    %\item Where $f = \left(1.5\dfrac{r_2}{r_1} + \dfrac{1}{1 + \dfrac{r_2}{r_1}}\right)^{-1}$
    \item Where $f = \left(1.5(r_2/r_1) + \dfrac{1}{1 + (r_2/r_1)}\right)^{-1}$
    \item and $r_1$ and $r_2$ are the radii of the solute and solvent molecules
    respectively.
  \end{itemize}

@@

  %MRS1: We want to be able to say that conclusions are independent of reasonable changes in the definition so
  %we are not picking and choosing results (either consciously or unconsciously) 
  Based on the geometric criteria proposed by Luzar and Chandler \cite{luzar_effect_1996},
  we determined a hydrogen bond to exist if the distance between the donor, D, and acceptor,
  A, atoms is less than 3.5 \AA~and the angle formed by D--H...A is less than 30\degree.
    %BJC: According to Luzar/Chandler: The range of a water molecule’s first coordination
    % shell is 3.5 Å, as determined from the oxygen-oxygen radial distribution function.
    % The amplitude of librations that break hydrogen bonds is ,~ 30 degrees, as estimated
    % from Debye-Waller factors
  \begin{itemize}
    \item Attempts to describe a hydrogen bond in the context of molecular simulations has
    yielded a number of definitions with no true consensus \cite{prada-gracia_quest_2013}.
	\item The geometry of hydrogen bonds has some dependence on the system being studied. 
    \item The definition of Luzar and Chandler is easily visualized for trajectories using
    the \texttt{hbonds} representation of the Visual Molecular Dynamics (VMD) software 
    package which allows us to directly check the validity of identified hydrogen bonds.
    \item We tested the sensitivity of our conclusions to this definition in 
    Section~\ref{S-section:hbond_sensitivity} of the SI.
    %BJC: might need to update this if something better exists for nitrogen 
  \end{itemize}

@@

  In contrast to our previous work with a solvent-free version of this membrane, the pore
  region of the 5 and 10 wt \% water systems are primarily filled with water and sodium
  ions.
  \begin{itemize}
    \item In dry systems, the pore center is densely filled with sodium ions and 
    head groups (See Ref~\cite{coscia_understanding_2019}).
    \item Figure~\ref{fig:component_densities} plots the densities of each
    membrane constituent.
    \item Water is densest at the center of each pore. 
    \item Sodium ions are densest between the pore center and the peak head group density.
    \item The peak density of sodium ions is not at the pore center in either case
    likely because they are still loosely associated with the monomer's 
    carboxylate head groups.
  \end{itemize}

  \noindent Pores in the 10 wt\% water system are wider and less crowded by monomers than
  those in the 5 wt\% water system.
  \begin{itemize}
    \item The peak head group density of 10 wt\% water systems is about 0.2 nm
    further from the pore center than the 5 wt\%
    \item The 5 wt \% water system has a non-negligible amount of tail group atoms
    that occupy the pore center.
  \end{itemize}

@@

  %MRS1: possibly include vertical dotted line to show where max head group peak occurs.
  %BJC1: tried it out. Seems like a good addition.
  \caption{The radial densities of various monomer components paint a picture of the
  pore topology where the pore centers are primarily composed of water and sodium ions.
  All RDFs represent the number of atoms located at a given distance from the pore center
  normalized by the volume of the annular bin 
  to which they belong. The 5 wt \% system (a) appears to be much more crowded by monomers
  than the 10 wt \% system (b). Head groups in (a) are densest about 0.2 nm closer to the
  pore center than in (b). A small amount of tail components find their way close to the 
  pore center of the 5 wt \% system.
  }\label{fig:component_densities}
  \end{figure}

@@

  \noindent Sodium coordinates with far less water molecules than it does in 
  bulk solution.
  \begin{itemize}
    \item Compared to 3.4 coordinated water molecules in bulk solution (see 
    section~\ref{method:coordination}), sodium ions in our system are, on average,
    coordinated to about 1.7 water molecules in the 10 wt \% system and 1.2 water
    molecules in the 5 wt\% system.
    \item The low levels of water coordination under confinement are likely driven
    in part by favorable interactions between sodium ions and carboxylate head groups.
    \item A dehydrated sodium ion is not shielded from the negatively charged 
    carboxylate group.~\cite{ma_drastically_2019}. 
    \item On average, sodium ions coordinate with 0.5 carboxylate group oxygen atoms in the
    10 wt \% water system and 0.4 carboxylate oxygen atoms in the 5 wt \% water system. 
    % BJC: I thought 5 wt \% might be a little higher. These numbers might be skewed by
    % sodium ions that are within cutoff of both carboxylate oxygen atoms. Might be
    % better to report average number of sodiums coordinated to a head group
  \end{itemize}

@@

  \noindent The MSDs are not a monotonic function of solute size.
  \begin{itemize}
  	\item We plotted the solute size against their MSDs in Figure~\ref{fig:msd_radius_5wt}
  	and~\ref{fig:msd_radius_10wt}.
  	\item Based on the Stokes-Einstein relationship, it is expected that
  	the solute MSDs should be inversely related to solute size.
  	\item Once solute and solvent are of comparable size, the relationship breaks
  	down and tends to underestimate the MSD. 
  	\item Gierer and Wirtz introduced a microfriction factor as theoretical
  	correction.
%  	\item It is expected that the Stokes-Einstein relationship, which assumes that 
%  	the solute radius is much larger than the solvent, should break down once
%  	solute and solvent are of comparable size.
  	\item Assuming that the Stokes-Einstein relationship is no longer valid 
  	for solutes with radius less than x nm, we fit the Stokes-Einstein relationship 
  	with and without the correction factor making sure that the two curves intersected
  	at x nm and that the corrected line passed through the highest MSD data point, methanol. %BJC1: need a justified value for x. Can also show its insensitivity to choice of intersection point.
  	\item We believe methanol is subject to the least hindrance due to its 
  	size 
  	\item Although both curves are approximations, they illustrate that
  	the majority of solutes in our study show lower than expected MSDs. 
%  	\item There are numerous examples of solutes in our study that do not 
%  	follow the behavior set forth by the Stokes-Einstein equation which 
%  	implies that solute MSD should be inversely related to solute size.  % citation
%    % MRS1: can you plot on the figure what the relatioship SHOULD look like?  It sort of looks linear-ish (especially 5).
%  	\item This behavior is not entirely surprising but worth emphasizing. 
	%BJC1: below moved to intro
%  	\item Membranes, including that studied here, are often characterized 
%  	with size-exclusion experiments which emphasizes selectivity based on the ability
%  	to enter a given pore. 
%  	\item Once we reach the nm to sub-nm pore size regime, size-exclusion 
%  	becomes of secondary importance since the primary purpose of these membranes is to 
%  	separate molecules whose sizes are on the same order as water.
%  	\item In order to handle complex waste streams with molecules of similar size,
%  	it is important to take advantage of material properties other than pore size. 
%  	\item Tetrose, our fifth largest solute, has an average MSD higher than more 
%  	than half of all solutes studied. 
%  	\item The two slowest solutes, DMF and THF, are smaller than 10 faster solutes.
%  	\item Transport is clearly affected by factors other than molecular size. 
  \end{itemize}

@@

  %BJC: need to check whether sodium ion association is exhibited by all solutes
  In addition to solute trapping in dense monomer regions, we observe a second
  trapping mechanism caused by preferential hydrogen bonding between 
  hydrogen bond donor solutes and monomer carboxylate groups. 
  %MRS1: is there a way we can deconvolute these two-three mechanisms?
  \begin{itemize}
    \item Of the time spent donating hydrogen atom(s), x \% of the hydrogen
    bonds occur between solutes and carboxylate groups as opposed to solutes
    with water. 
    \item This shows a high preference for the carboxylate anions since there
    are 5 times more water molecules in the system.
    %MRS1: carboxylate also has net negative charge - not just higher negative partial charge,
    %also no extra neutralizing positive partial charge nearby.
    \item The carboxylate oxygen atoms have a slightly higher partial negative
    charge than water molecules.
    \item Additionally, on average, each sodium ion is coordinated to 1.7 water
    molecules. Roughly all of the water in the pore region is usually coordinated
    to a sodium ion which decreases their availability to solutes.
    %MRS1: this should lead to reduced ability to solvate positive things, but shouldn't reduce H-boonding that much?
  \end{itemize}

  Finally, we see instances of solutes which become immobilized or slowed by 
  association with sodium counterions. 
  \begin{itemize}
    \item Much like water, the polarity of the solutes leaves partial negative
    charges which are stabilized through electrostatic interactions with sodium ions.
    \item There are many cases in which polar groups bind to sodium ions for at
    %MRS1: a 'few times steps' seems irrelevant.   
    least a few time steps. 
    \item There are some cases where solutes become immobilized for long periods
    of time while in close proximity to a sodium ion.
    \item In Figure~\ref{fig:na_met_trace}, the oxygen atom of methanol stays
    within 2.5 \AA of a sodium ion for the entire length of a trapping occurence.
  \end{itemize}

  \begin{figure}[!htb]
  \centering
  \includegraphics[width=0.45\textwidth]{na_met_trace.pdf}
  \caption{The oxygen atom of methanol stays bound to the same sodium ion for
  the majority of the trapping occurence between 400 and 600 ns. Regions
  highlighted red or blue indicate times when methanol's oxygen atom is within 
  2.5 \AA~of a sodium ion. The color of the shaded regions is switched every time
  the oxygen atom becomes associated to a different sodium ion.}\label{fig:na_met_trace}
  \end{figure}

  %MRS1: I think maybe we want to keep this minimal. 
  \noindent The hopping and trapping mechanism exhibited by all solutes is characteristic of
  a continuous time random walk (CTRW) model.	
  \begin{itemize}
  	\item The length of entrapment follows a power law distribution 
  	(Figure~\ref{fig:example_powerlaw}) and the distribution of hop lengths can be 
  	described with a Gaussian distribution (Figure~\ref{fig:example_hop_dist}).
  	\item Power law distributed dwell times are responsible for the ageing phenomenon
  	which causes the slope of the MSD curve to decrease with increasing measurement
  	time because longer dwell times are sampled.  %BJC: might need to reword this a bit 
 	\item Although these observed distributions strongly support a CTRW model, the time-averaged
 	MSD of a pure CTRW should be linear which is not the case.~\cite{neusius_subdiffusion_2008,meroz_subdiffusion_2010}
  \end{itemize}

%  \noindent The direction of each hop is anti-correlated to the direction of the previous hop.
  \noindent Transport may be better described by a subordinated fractional brownian motion 
  (sFBM) model.
  \begin{itemize}
  	\item Figure~\ref{fig:example_autocovariance} shows the autocovariance function of 
  	ethanol step vectors. % BJC: vectors because includes magnitude + direction. Is there a better word?
  	\item The negative autocovariance at low values of k indicates anti-correlation
  	between hops. 
  	\item If solutes followed a pure CTRW mechanism, the autocovariance function would
  	decay to zero immediately.
  	\item Although the autocovariance function is relatively noise, due to the somewhat small
  	number of hops observed over the course of each solute trajectory, there is the least 
  	uncertainty at k=1, the most insightful data point. This behavior is consistent across
  	all solutes molecules. % Can put error bars on points
  	\item Therefore, we believe transport can be described as subordinated fractional Brownian
  	motion where the leading process is a CTRW with hops whose direction is dictated by the parent
  	process, FBM.
  	\item Future publications will focus on modeling the solute's transport characteristics
  	with an sFBM model
  	\item We will draw on these observations only in a qualitative sense for the remainder of this work.
  \end{itemize}

  %BJC: seems like the MSD becomes linear at long times. Perhaps due to loss of memory with time.

  \begin{figure}
  \centering
  \begin{subfigure}{0.325\textwidth}
  \includegraphics[width=\linewidth]{example_powerlaw.pdf}
  \caption{}\label{fig:example_powerlaw}
  \end{subfigure}
  \begin{subfigure}{0.325\textwidth}
  \includegraphics[width=\linewidth]{example_hop_dist.pdf}
  \caption{}\label{fig:example_hop_dist}
  \end{subfigure}
  \begin{subfigure}{0.325\textwidth}
  \includegraphics[width=\linewidth]{example_autocovariance.pdf}
  \caption{}\label{fig:example_autocovariance}
  \end{subfigure}
  \caption{(a) The distribution of dwell times resembles a power law distribution. 
  (b) The distribution of hop lengths appears Gaussian. (c) Hops are anti-correlated
  to their previous hop as indicated by the negative value of the autocovariance 
  function at $k$ = 1.}\label{fig:examples}
  \end{figure}

  \noindent The transport behavior exhibited by solutes in the 5 wt \% water systems
  is similar to those shown by those in the 10 wt \% system however the timescales are
  much longer.
  \begin{itemize}
    %BJC: will put supporting data in supporting information
    \item We observe subdiffusive behavior with intermittent hopping between
    periods of entrapment.
    \item The frequency and length of hops are both diminished in the 5 wt \% system.
    \item Since there are only 24 solute molecules in each system, in order to obtain
    better time-averaged descriptions of solute transport mechanisms, we will focus
    the rest of our analysis on transport in the 10 wt \% water systems.
  \end{itemize}

@@

  The MSD of methanol, ethanol, propanol and butanol descends in order of 
  their molecular weight, however, methanol travels faster than expected.  %BJC: find approximate relationship between MW and mobility
  \begin{itemize}
    \item The MSD of ethanol, propanol and butanol descend approximately
    linearly as expected from the Stokes-Einstein relationship  % BJC: maybe better to use wilke-chang version with correction factor
    \item However, methanol travels considerably faster than suggested by the
    relationship. (See Figure~\ref{fig:msd_radius_simple_alcohol_rdf}
  \end{itemize}

@@

  All simple alcohols participate in a similar number of hydrogen bonding interactions
  with the monomer head groups, but with varying preference towards hydrogen bonds with
  the monomer carboxylate oxygen atoms (See Figure~\ref{fig:simple_alcohol_hbonds}) caused
  by increasing hydrophobic character.
  \begin{itemize}
  	\item If all 5 hydrogen bonding acceptor sites on the monomer head groups were equal,
  	we would expect the ratio of the number of hydrogen bonds between solutes and the two 
  	carboxylate oxygen atoms to the number of hydrogen bonds between solutes and the three
  	ether groups to be 2/3. 
  	\item There is a clear preference towards hydrogen bonding with the carboxylate 
  	oxygen atoms for all simple alcohols.
  	\item This is largely due to the more highly crowded environment surrounding the ether
  	oxygen atoms combined with their lower partial charges.
        %MRS1: also carboxylate has larger net charge.
        %MRS1: note the partial chage is a moel thing
  	\item Butanol shows the largest preference towards hydrogen bonds with carboxylate 
  	head groups.
  	\item The radial distribution function of atoms located at opposite ends of butanol
  	shows that, on average, oxygen atoms are situated 0.25 nm closer to the pore centers
  	than the distal carbon atoms.
  	\item This suggests that alcohols tend to orient themselves like the liquid crystal 
  	monomers, with hydrophilic components point towards the pore centers.
  	\item When solutes are buried in the pore walls, their MSDs are shorter.
        %MRS1: is there enough data to establish this? How will it be graphed?  
  \end{itemize}

>>>>

  The Stokes-Einstein relationship expresses the diffusion coefficient of 
  a hard spherical particle as a function that is inversely related to the
  particle's radius:
  \begin{itemize}
  	\item $D = \dfrac{k_bT}{6\pi\eta r}$
  	\item where $k_b$ and $T$ are the Boltzmann	constant and the system 
  	temperature respectively and $\eta$ is the system's viscosity.
  	\item For the largely demonstrative calculations relevant to this study, 
  	we assume that the system viscosity is constant since we only make minor
  	changes to the membrane's composition and accurately assessing the viscosity
  	in a complex and inhomogeneous system such as ours is a challenge by itself.
  	\item Additionally, rather than calculate $D$, we will apply the relationship
  	to analyze solute MSDs, which is valid because all trajectories are of the same
  	length.
  \end{itemize}

  \noindent It is well-known that the relationship breaks down when solute size becomes
  on the order of solvent size because the solute can no longer be treated
  as a non-interacting hard sphere. % citation
  \begin{itemize}
    \item Gierer and Wirtz introduced a microfriction correction factor in order to 
    address this issue. 
    \item They proposed that $D = \dfrac{k_bT}{6\pi\eta fr}$
    %\item Where $f = \left(1.5\dfrac{r_2}{r_1} + \dfrac{1}{1 + \dfrac{r_2}{r_1}}\right)^{-1}$
    \item Where $f = \left(1.5(r_2/r_1) + \dfrac{1}{1 + (r_2/r_1)}\right)^{-1}$
    \item and $r_1$ and $r_2$ are the radii of the solute and solvent molecules
    respectively.
  \end{itemize}

@@

  %MRS1: We want to be able to say that conclusions are independent of reasonable changes in the definition so
  %we are not picking and choosing results (either consciously or unconsciously) 
  Based on the geometric criteria proposed by Luzar and Chandler \cite{luzar_effect_1996},
  we determined a hydrogen bond to exist if the distance between the donor, D, and acceptor,
  A, atoms is less than 3.5 \AA~and the angle formed by D--H...A is less than 30\degree.
    %BJC: According to Luzar/Chandler: The range of a water molecule’s first coordination
    % shell is 3.5 Å, as determined from the oxygen-oxygen radial distribution function.
    % The amplitude of librations that break hydrogen bonds is ,~ 30 degrees, as estimated
    % from Debye-Waller factors
  \begin{itemize}
    \item Attempts to describe a hydrogen bond in the context of molecular simulations has
    yielded a number of definitions with no true consensus \cite{prada-gracia_quest_2013}.
	\item The geometry of hydrogen bonds has some dependence on the system being studied. 
    \item The definition of Luzar and Chandler is easily visualized for trajectories using
    the \texttt{hbonds} representation of the Visual Molecular Dynamics (VMD) software 
    package which allows us to directly check the validity of identified hydrogen bonds.
    \item In section~\ref{S-section:hbond_sensitivity} of the SI, we show that our 
    conclusions are insensitive to this definition within a reasonable range.
    %BJC: might need to update this if something better exists for nitrogen 
  \end{itemize}

@@

  In contrast to our previous work with a solvent-free version of this membrane, the pore
  region of the 5 and 10 wt \% water systems are primarily filled with water and sodium
  ions.
  \begin{itemize}
    \item In dry systems, the pore center is densely filled with sodium ions and 
    head groups (See Ref~\cite{coscia_understanding_2019}).
    \item Figure~\ref{fig:component_densities} plots the densities of each
    membrane constituent in the 5 and 10 wt \% systems.
    \item Water is densest at the center of each pore. 
    \item Sodium ions are densest between the pore center and the peak head group density (black dashed line).
    \item The peak density of sodium ions is not at the pore center in either case
    likely because they are still loosely associated with the monomer's 
    carboxylate head groups.
  \end{itemize}

  \noindent Pores in the 10 wt\% water system are wider and less crowded by monomers than
  those in the 5 wt\% water system.
  \begin{itemize}
    \item The peak head group density of 10 wt\% water systems is about 0.2 nm
    further from the pore center than the 5 wt\%
    \item The 5 wt \% water system has a non-negligible amount of tail group atoms
    that occupy the pore center.
    \item Based on these observations, we expect solute transport to be fastest 
    in the 10 wt \% system.
  \end{itemize}

@@

  %MRS1: possibly include vertical dotted line to show where max head group peak occurs.
  %BJC1: tried it out. Seems like a good addition.
  \caption{The radial densities of various monomer components paint a picture of the
  pore topology where the pore centers are primarily composed of water and sodium ions.
  All RDFs represent the number of atoms located at a given distance from the pore center
  normalized by the volume of the annular bin to which they belong. The pores of the 5 
  wt \% system (a) appears to be much more crowded by monomers than the 10 wt \% system (b).
  Head groups in (a) are densest about 0.2 nm closer to the pore center than in (b). 
  A small amount of tail components find their way close to the pore center of the 5 wt \% system.
  }\label{fig:component_densities}
  \end{figure}

@@

  \noindent Sodium coordinates with far less water molecules than it does in 
  bulk solution.
  \begin{itemize}
    \item Compared to 3.4 coordinated water molecules in bulk solution (see 
    section~\ref{method:coordination}), sodium ions in our system are, on average,
    coordinated to about 1.7 water molecules in the 10 wt \% system and 1.2 water
    molecules in the 5 wt\% system.
    \item The low levels of water coordination under confinement are likely driven
    in part by favorable interactions between sodium ions and carboxylate head groups.
    \item A dehydrated sodium ion is not well shielded from the negatively charged 
    carboxylate group.~\cite{ma_drastically_2019}. 
    \item On average, sodium ions coordinate with 0.5 carboxylate group oxygen atoms in the
    10 wt \% water system and 0.4 carboxylate oxygen atoms in the 5 wt \% water system. 
    % BJC: I thought 5 wt \% might be a little higher. These numbers might be skewed by
    % sodium ions that are within cutoff of both carboxylate oxygen atoms. Might be
    % better to report average number of sodiums coordinated to a head group
  \end{itemize}

@@

  \noindent The MSDs depend on more than just solute size.
  \begin{itemize}
  	\item We plotted the solute size against their MSDs in Figure~\ref{fig:msd_radius_5wt}
  	and~\ref{fig:msd_radius_10wt}.
%  	\item Based on the Stokes-Einstein relationship, it is expected that
%  	the solute MSDs should be inversely related to solute size.
%  	\item Once solute and solvent are of comparable size, the relationship breaks
%  	down and tends to underestimate the MSD. 
%  	\item Gierer and Wirtz introduced a microfriction factor as theoretical
%  	correction.
%  	\item It is expected that the Stokes-Einstein relationship, which assumes that 
%  	the solute radius is much larger than the solvent, should break down once
%  	solute and solvent are of comparable size.
  	\item Assuming that the Stokes-Einstein relationship is no longer valid 
  	for solutes with a radius less than x nm, we fit the Stokes-Einstein relationship 
  	with and without the correction factor making sure that the two curves intersected
  	at x nm and that the corrected line passed through the highest MSD data point, methanol. %BJC1: need a justified value for x. Can also show its insensitivity to choice of intersection point.
  	\item We believe methanol is subject to the least hindrance due its small
  	size and relatively fast motion.
  	\item Although both curves are approximations, they illustrate that
  	the majority of solutes in our study show lower than expected MSDs. 
  	\item In most cases, the predicted MSDs even fall below the 
  	conservative Stokes-Einstein estimate.
  	\item It is clear that more complex mechanisms determine the MSDs of
  	these solutes.
%  	\item There are numerous examples of solutes in our study that do not 
%  	follow the behavior set forth by the Stokes-Einstein equation which 
%  	implies that solute MSD should be inversely related to solute size.  % citation
%    % MRS1: can you plot on the figure what the relatioship SHOULD look like?  It sort of looks linear-ish (especially 5).
%  	\item This behavior is not entirely surprising but worth emphasizing. 
	%BJC1: below moved to intro
%  	\item Membranes, including that studied here, are often characterized 
%  	with size-exclusion experiments which emphasizes selectivity based on the ability
%  	to enter a given pore. 
%  	\item Once we reach the nm to sub-nm pore size regime, size-exclusion 
%  	becomes of secondary importance since the primary purpose of these membranes is to 
%  	separate molecules whose sizes are on the same order as water.
%  	\item In order to handle complex waste streams with molecules of similar size,
%  	it is important to take advantage of material properties other than pore size. 
%  	\item Tetrose, our fifth largest solute, has an average MSD higher than more 
%  	than half of all solutes studied. 
%  	\item The two slowest solutes, DMF and THF, are smaller than 10 faster solutes.
%  	\item Transport is clearly affected by factors other than molecular size. 
  \end{itemize}

@@

  In addition to solute trapping in dense monomer regions, we observe a second
  trapping mechanism caused by preferential hydrogen bonding between 
  hydrogen bond donor solutes and monomer head groups. 
  %MRS1: is there a way we can deconvolute these two-three mechanisms?
  \begin{itemize}
    \item To continue with our ethanol example, we observe that the 24 ethanol 
    molecules donate an average of 15.7 hydrogen bonds per frame and accept 
    0.6 hydrogen bonds per frame.
    % BJC1: 6.33 hbonds between EtOH and COOH per frame, 3.84 b/w EtOH and 
    % ether oxygen, 5.56 between EtOH and HOH (where Ethanol donates)
    \item On average, 40 \% of hydrogen bonds donated by ethanol go to 
    carboxylate head groups, 25 \% go to the ether linkages between the tails and
    the head groups and the remaining 35 \% to water.
%    \item This is significant because there are many more water molecules in
%    the pores than there are carboxylate groups.  
%    \item Of the time spent donating hydrogen atom(s), 53 \% of the hydrogen
%    bonds occur between solutes and carboxylate groups as opposed to solutes
%    with water. 
%    \item This shows a high preference for the carboxylate anions since there
%    are 5 times more water molecules in the system.  % BJC1: more like 3 times more water molecules because many are in the tails.
    %MRS1: carboxylate also has net negative charge - not just higher negative partial charge,
    %also no extra neutralizing positive partial charge nearby.
    \item There are less carboxylate oxygen atoms in the pore than there are water
    molecules yet more hydrogen bonds are donated to them.
    \item The stability of hydrogen bonds with carboxylate oxygen atoms is likely
    high since the oxygen atoms have a negative charge with no neutralizing positive
    charges nearby.
    \item Additionally, on average, each sodium ion is coordinated to 1.7 water
    molecules meaning an appreciable fraction of the water molecules occupying 
    the pore region are usually coordinated to a sodium ion which decreases 
    their availability to accept hydrogen bonds from solutes.
    % MRS1: this should lead to reduced ability to solvate positive things, but 
    % shouldn't reduce H-bonding that much?
    % BJC1: I think that it takes away acceptor oxygen atoms since they are occupied
    % by sodium. The hydrogen atoms of water could still hbond but I'm just talking
    % about ethanol donating to water, for which opportunities should be suppressed.
  \end{itemize}

  Finally, we see instances of solutes that become immobilized or slowed by 
  association with sodium counterions. 
  \begin{itemize}
    \item Much like water, the polarity of the solutes creates regions of high
    electron density, modeled using partial negative charges, which are stabilized
    through electrostatic interactions with sodium ions.
    \item There are many cases in which polar groups bind to sodium ions for at
    least a short period of time. 
    \item There are some cases where solutes become immobilized for long periods
    of time while in close proximity to a sodium ion.
    \item In Figure~\ref{fig:na_met_trace}, the oxygen atom of methanol stays
    within 2.5 \AA~of a sodium ion for the entire length of a trapping occurence.
  \end{itemize}

  \begin{figure}[!htb]
  \centering
  \includegraphics[width=0.45\textwidth]{na_met_trace.pdf}  % create with nn.py located in MET/10wt
  \caption{The oxygen atom of methanol stays within 2.5 \AA~of the same sodium ion for
  the majority of the trapping occurence between 400 and 600 ns. Regions
  highlighted red or blue indicate times when methanol's oxygen atom is within 
  2.5 \AA~of a sodium ion. The color of the shaded regions are switched every time
  the oxygen atom becomes associated to a different sodium ion.}\label{fig:na_met_trace}
  \end{figure}

  %MRS1: I think maybe we want to keep this minimal. 
  %BJC1: Leaving out for now
%  \noindent The hopping and trapping mechanism exhibited by all solutes is characteristic of
%  a continuous time random walk (CTRW) model.	
%  \begin{itemize}
%  	\item The length of entrapment follows a power law distribution 
%  	(Figure~\ref{fig:example_powerlaw}) and the distribution of hop lengths can be 
%  	described with a Gaussian distribution (Figure~\ref{fig:example_hop_dist}).
%  	\item Power law distributed dwell times are responsible for the ageing phenomenon
%  	which causes the slope of the MSD curve to decrease with increasing measurement
%  	time because longer dwell times are sampled.  %BJC: might need to reword this a bit 
% 	\item Although these observed distributions strongly support a CTRW model, the time-averaged
% 	MSD of a pure CTRW should be linear which is not the case.~\cite{neusius_subdiffusion_2008,meroz_subdiffusion_2010}
%  \end{itemize}
%  
%%  \noindent The direction of each hop is anti-correlated to the direction of the previous hop.
%  \noindent Transport may be better described by a subordinated fractional brownian motion 
%  (sFBM) model.
%  \begin{itemize}
%  	\item Figure~\ref{fig:example_autocovariance} shows the autocovariance function of 
%  	ethanol step vectors. % BJC: vectors because includes magnitude + direction. Is there a better word?
%  	\item The negative autocovariance at low values of k indicates anti-correlation
%  	between hops. 
%  	\item If solutes followed a pure CTRW mechanism, the autocovariance function would
%  	decay to zero immediately.
%  	\item Although the autocovariance function is relatively noise, due to the somewhat small
%  	number of hops observed over the course of each solute trajectory, there is the least 
%  	uncertainty at k=1, the most insightful data point. This behavior is consistent across
%  	all solutes molecules. % Can put error bars on points
%  	\item Therefore, we believe transport can be described as subordinated fractional Brownian
%  	motion where the leading process is a CTRW with hops whose direction is dictated by the parent
%  	process, FBM.
%  	\item Future publications will focus on modeling the solute's transport characteristics
%  	with an sFBM model
%  	\item We will draw on these observations only in a qualitative sense for the remainder of this work.
%  \end{itemize}
%  
%  %BJC: seems like the MSD becomes linear at long times. Perhaps due to loss of memory with time.
%
%  \begin{figure}
%  \centering
%  \begin{subfigure}{0.325\textwidth}
%  \includegraphics[width=\linewidth]{example_powerlaw.pdf}
%  \caption{}\label{fig:example_powerlaw}
%  \end{subfigure}
%  \begin{subfigure}{0.325\textwidth}
%  \includegraphics[width=\linewidth]{example_hop_dist.pdf}
%  \caption{}\label{fig:example_hop_dist}
%  \end{subfigure}
%  \begin{subfigure}{0.325\textwidth}
%  \includegraphics[width=\linewidth]{example_autocovariance.pdf}
%  \caption{}\label{fig:example_autocovariance}
%  \end{subfigure}
%  \caption{(a) The distribution of dwell times resembles a power law distribution. 
%  (b) The distribution of hop lengths appears Gaussian. (c) Hops are anti-correlated
%  to their previous hop as indicated by the negative value of the autocovariance 
%  function at $k$ = 1.}\label{fig:examples}
%  \end{figure}

  \noindent The transport behavior exhibited by solutes in the 5 wt \% water systems
  is similar to that shown by those in the 10 wt \% system however the timescales are
  much longer.
  \begin{itemize}
    %BJC: will put supporting data in supporting information
    \item We observe subdiffusive behavior with intermittent hopping between
    periods of entrapment.
    \item The frequency and length of hops are both diminished in the 5 wt \% system.
    \item Since there are only 24 solute molecules in each system, in order to obtain
    better time-averaged descriptions of solute transport mechanisms, we will focus
    the rest of our analysis on transport in the 10 wt \% water systems.
  \end{itemize}

@@

%  The MSD of methanol, ethanol, propanol and butanol descends in order of 
%  their size, however, the.
%  \begin{itemize}
%    \item The MSD of ethanol, propanol and butanol descend approximately
%    linearly as expected from the Stokes-Einstein relationship  % BJC: maybe better to use wilke-chang version with correction factor
%    \item However, methanol travels considerably faster than suggested by the
%    relationship. (See Figure~\ref{fig:msd_radius_simple_alcohol_rdf}
%  \end{itemize}

  The MSDs of methanol, ethanol, propanol and butanol descend in order of 
  their size.
  \begin{itemize}
    \item Using methanol as a reference, the other alcohols move slower than
    expected according to both the pure Stokes-Einstein relationship and the
    corrected relationship (See Figure~\ref{fig:msd_radius_simple_alcohol_rdf}).
  \end{itemize}

@@

  All simple alcohols participate in a similar number of hydrogen bonding interactions
  with the monomer head groups, but with varying preference towards hydrogen bonds with
  the monomer carboxylate oxygen atoms over the ether oxygen atoms (See Figure~\ref{fig:simple_alcohol_hbonds})
  % caused by increasing hydrophobic character.
  \begin{itemize}
  	\item If all 5 hydrogen bonding acceptor sites on the monomer head groups were equal,
  	we would expect the ratio of the number of hydrogen bonds between solutes and the two 
  	carboxylate oxygen atoms to the number of hydrogen bonds between solutes and the three
  	ether groups to be 2/3. 
  	\item There is a clear preference towards hydrogen bonding with the carboxylate 
  	oxygen atoms for all simple alcohols.
  	\item This is largely due to the large net charge of the carboxylate groups as well
  	as the more highly crowded environment surrounding the ether oxygen atoms. % combined with their lower electron density. % partial charges.
  	\item Butanol shows the largest preference towards hydrogen bonds with carboxylate 
  	head groups.
  	\item The radial distribution function of atoms located at opposite ends of butanol
  	shows that, on average, oxygen atoms are situated 0.25 nm closer to the pore centers
  	than the distal carbon atoms.
  	\item This suggests that alcohols tend to orient themselves like the liquid crystal 
  	monomers, with hydrophilic components point towards the pore centers.
  	%\item When solutes are buried in the pore walls, their MSDs are shorter.
  \end{itemize}

  \begin{figure}
  \centering
  %BJC1: I'm not sure of figure (a) is necessary
  \begin{subfigure}{0.45\textwidth}
  \includegraphics[width=\linewidth]{msd_radius_simple_alcohols_10wt.pdf}
  \caption{}\label{fig:msd_radius_simple_alcohol_rdf}
  \end{subfigure}
  \begin{subfigure}{0.45\textwidth}
  \includegraphics[width=\linewidth]{simple_alcohol_rdf.pdf}
  \caption{}\label{fig:simple_alcohol_rdf}
  \end{subfigure}
  \begin{subfigure}{0.45\textwidth}
  \includegraphics[width=\linewidth]{simple_alcohol_hbonds.pdf}
  \caption{}\label{fig:simple_alcohol_hbonds}
  \end{subfigure}
  \begin{subfigure}{0.45\textwidth}
  \includegraphics[width=\linewidth]{butanol_CO.pdf}\lapbox[\width]{-2.85cm}{\raisebox{3cm}{\includegraphics[height=1.4cm]{butanol_labeled.pdf}}}
  \caption{}\label{fig:butanol_CO}
  \end{subfigure}
  %MRS: label the black line (tails? heads?)
  \caption{(a) The MSD of the simple alcohols decrease as a function of the solute size, however
  methanol's MSD is considerably higher than expected based on the Stokes-Einstein equation. 
  (b) The radial distribution functions of each simple alcohol shows a maximum close
  to the highest density of monomer head groups (dashed line, normalized for easier visual
  comparison). Methanol spends the largest proportion of time, relative to the other alcohols,
  near the pore center, which may help explain its fast dynamics. (c) Despite relatively little
  difference in the total number of active hydrogen bonds per frame, a given alcohol's preference
  towards hydrogen bonds with the carboxylate groups increases with molecule size. (d) The average
  location of butanol's oxygen atom is significantly closer to the pore center than its most distal
  carbon atom, suggesting that the molecule is oriented with hydrophobic tails pointing away from
  the pore center.}\label{fig:simple_alcohols}
  \end{figure}
